% Created 2019-04-02 Tue 21:34
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{minted}
\author{Ethan Johnston}
\date{\today}
\title{Configuration Files}
\hypersetup{
 pdfauthor={Ethan Johnston},
 pdftitle={Configuration Files},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.2.2 (Org mode 9.2.2)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{About}
\label{sec:orgcd02a43}
\begin{itemize}
\item This repository is mostly just for the purposes of hosting my spacemacs config.
\item Just in case I'll document any of the additional keybindings or functionality that I've added.
\end{itemize}
\section{Spacemacs}
\label{sec:org0341940}
\subsection{Defaults}
\label{sec:org6f0210c}
My configuration is pretty bare bones right now. I've enabled a lot of the useful layers that aren't automatically
turned on (auto-completion, spellcheck, syntax check, etc.). Outside of this I've enabled some QOL features that I
personally prefer having on like line numbers and slanted style for the modeline.
\subsection{User Config}
\label{sec:org02dace0}
\subsubsection{Org-mode}
\label{sec:org273c2a3}
I've included some org-mode configuration here mostly. One thing I really like is having syntax highlighting 
in the pdf output from org files. You can achieve this with the following snippet I got from a TA of mine.
\begin{minted}[]{elisp}
(setq org-latex-listings 'minted
          org-latex-packages-alist '(("" "minted"))
          org-latex-pdf-process
          '("pdflatex -shell-escape -interaction nonstopmode -output-directory %o %f"
            "biber %b"
            "pdflatex -shell-escape -interaction nonstopmode -output-directory %o %f")
)
\end{minted}
If for some reason you are looking to use this .spacemacs setup, be aware
that minted has dependencies and will most likely crash you pdf export if you don't have them. You'll want
to make sure you've got python and the pygments package installed (see \href{http://pygments.org/download/}{installation}). If that doesn't work
the issue is with your latex packages not with emacs itself (as I've learned the hard way).

Outside of this there some added support for haskell code blocks I've included, and snippets for haskell and C
source blocks.
\subsubsection{Keybindings}
\label{sec:org70e4cf7}
\begin{itemize}
\item \texttt{SPC e '} opens the eshell in your current buffer.
\item \texttt{SPC y r} will reload your snippets.
\item \texttt{SPC y n} will open a new snippet.
\end{itemize}
\end{document}